Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
Future Work

>>>>

There are a few ways that we can expand on {\em Kimbee}. We plan on deploying the project for use in the Arlington Public School District to see how children respond and learn from {\em Kimbee} along with how experienced speech therapists use {\em Kimbee} to aid the therapy process. Along with this, we can also expand on the application itself by targeting speech sounds past the `R' and `W' sound replacement. We can also enhance the child's experience by adding more mini games for the child to play and a token system for children to spend the honey they collect on aesthetics for the bee character.
